Properties of Winning Iterated Prisoner's Dilemma Strategies.

### 2023-12-01 paper/perfomances_table.tex
working on main paper for the special issue

\begin{tabular}{lllllllll}
\toprule
{} &                     Name & \$\textbackslash bar\{r\}\$ &                       Name & \$\textbackslash bar\{r\}\$ &                       Name & \$\textbackslash bar\{r\}\$ &                       Name & \$\textbackslash bar\{r\}\$ \\
\midrule
0  &            Evolved HMM 5 &     0.007 &                       MEM2 &     0.061 &             Evolved FSM 16 &       0.0 &                   Defector &     0.006 \\
1  &           Evolved FSM 16 &      0.01 &       Spiteful Tit For Tat &     0.063 &    Evolved FSM 16 Noise 05 &     0.013 &          Better and Better &     0.011 \\
2  &     EvolvedLookerUp2\_2\_2 &     0.011 &           Nice Meta Winner &     0.066 &                       MEM2 &     0.027 &                 Aggravater &     0.014 \\
3  &  Evolved FSM 16 Noise 05 &     0.017 &                    Grudger &     0.067 &              Evolved HMM 5 &     0.043 &                  Fortress4 &     0.021 \\
4  &        PSO Gambler 2\_2\_2 &     0.022 &    Meta Winner Long Memory &     0.073 &       EvolvedLookerUp2\_2\_2 &     0.049 &            Tricky Defector &     0.038 \\
5  &              Evolved ANN &     0.029 &                   Forgiver &     0.074 &       Spiteful Tit For Tat &     0.059 &    Meta Winner Long Memory &     0.049 \\
6  &            Evolved ANN 5 &     0.034 &               Fool Me Once &     0.074 &           Nice Meta Winner &     0.069 &     Meta Winner Memory One &      0.05 \\
7  &        PSO Gambler 1\_1\_1 &     0.037 &                Meta Winner &     0.075 &         NMWE Finite Memory &     0.069 &  Meta Winner Finite Memory &      0.05 \\
8  &            Evolved FSM 4 &     0.049 &     Meta Winner Memory One &     0.076 &         NMWE Deterministic &      0.07 &     Meta Winner Stochastic &     0.051 \\
9  &         PSO Gambler Mem1 &      0.05 &  Meta Winner Finite Memory &     0.077 &                    Grudger &      0.07 &  Meta Winner Deterministic &     0.052 \\
10 &                 Winner12 &      0.06 &  Meta Winner Deterministic &     0.078 &           NMWE Long Memory &     0.074 &                Meta Winner &     0.053 \\
11 &             Fool Me Once &     0.061 &         NMWE Deterministic &     0.087 &  Nice Meta Winner Ensemble &     0.076 &       Meta Winner Ensemble &     0.059 \\
12 &                      DBS &     0.071 &           NMWE Long Memory &     0.087 &       EvolvedLookerUp1\_1\_1 &     0.077 &                  Fortress3 &      0.07 \\
13 &            DoubleCrosser &     0.072 &         CollectiveStrategy &     0.087 &            NMWE Memory One &      0.08 &         CollectiveStrategy &     0.077 \\
14 &              BackStabber &     0.075 &                   Defector &     0.089 &            NMWE Stochastic &     0.085 &                   Prober 3 &      0.08 \\
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{lllllllll}
\toprule
{} &                     Name & \$\textbackslash bar\{r\}\$ &                        Name & \$\textbackslash bar\{r\}\$ &                       Name & \$\textbackslash bar\{r\}\$ &                       Name & \$\textbackslash bar\{r\}\$ \\
\midrule
0  &            Evolved HMM 5 &     0.007 &                         DBS &       0.0 &             Evolved FSM 16 &       0.0 &                     Raider &     0.022 \\
1  &           Evolved FSM 16 &      0.01 &     Evolved FSM 16 Noise 05 &     0.008 &    Evolved FSM 16 Noise 05 &     0.013 &                       MEM2 &     0.037 \\
2  &     EvolvedLookerUp2\_2\_2 &     0.011 &      Evolved ANN 5 Noise 05 &     0.013 &                       MEM2 &     0.027 &                   Prober 3 &     0.039 \\
3  &  Evolved FSM 16 Noise 05 &     0.017 &                 BackStabber &     0.024 &              Evolved HMM 5 &     0.043 &    Evolved FSM 16 Noise 05 &     0.048 \\
4  &        PSO Gambler 2\_2\_2 &     0.022 &               DoubleCrosser &     0.025 &       EvolvedLookerUp2\_2\_2 &     0.049 &                Hard Prober &     0.072 \\
5  &              Evolved ANN &     0.029 &               Evolved ANN 5 &     0.028 &       Spiteful Tit For Tat &     0.059 &       Spiteful Tit For Tat &     0.078 \\
6  &            Evolved ANN 5 &     0.034 &                 Evolved ANN &     0.038 &           Nice Meta Winner &     0.069 &          Better and Better &     0.089 \\
7  &        PSO Gambler 1\_1\_1 &     0.037 &        Spiteful Tit For Tat &     0.051 &         NMWE Finite Memory &     0.069 &                    Grudger &     0.091 \\
8  &            Evolved FSM 4 &     0.049 &               Evolved HMM 5 &     0.051 &         NMWE Deterministic &      0.07 &                  Fortress4 &     0.096 \\
9  &         PSO Gambler Mem1 &      0.05 &              Level Punisher &     0.052 &                    Grudger &      0.07 &     Meta Winner Memory One &     0.099 \\
10 &                 Winner12 &      0.06 &                   Omega TFT &     0.059 &           NMWE Long Memory &     0.074 &           NMWE Long Memory &     0.099 \\
11 &             Fool Me Once &     0.061 &                Fool Me Once &     0.059 &  Nice Meta Winner Ensemble &     0.076 &           Nice Meta Winner &     0.104 \\
12 &                      DBS &     0.071 &  PSO Gambler 2\_2\_2 Noise 05 &     0.067 &       EvolvedLookerUp1\_1\_1 &     0.077 &         NMWE Deterministic &     0.109 \\
13 &            DoubleCrosser &     0.072 &              Evolved FSM 16 &     0.078 &            NMWE Memory One &      0.08 &            NMWE Memory One &     0.112 \\
14 &              BackStabber &     0.075 &                  EugineNier &      0.08 &            NMWE Stochastic &     0.085 &  Nice Meta Winner Ensemble &     0.115 \\
\bottomrule
\end{tabular}

### 2023-12-01 paper/top_perfomances.tex
working on main paper for the special issue

\begin{tabular}{lggllggllr}
\toprule
& \multicolumn{2}{g}{Standard} & \multicolumn{2}{c}{Noisy} & \multicolumn{2}{g}{Probabilistic ending} &  \multicolumn{2}{c}{Noisy probabilistic ending} \\
\midrule
& Name & $\bar{r}$ &                 Name & $\bar{r}$ &               Name & $\bar{r}$ &                 Name & $\bar{r}$ \\
\midrule
0  &            Evolved HMM 5 &   0.00667 &                 Grumpy &   0.14020 &          Fortress4 &   0.01266 &           Alternator &   0.30370 \\
1  &           Evolved FSM 16 &   0.00995 &                    $e$ &   0.19388 &           Defector &   0.01429 &               $\phi$ &   0.30978 \\
2  &     EvolvedLookerUp2 2 2 &   0.01064 &         Tit For 2 Tats &   0.20617 &  Better and Better &   0.01587 &                  $e$ &   0.31250 \\
3  &  Evolved FSM 16 Noise 05 &   0.01667 &  Slow Tit For Two Tats &   0.20962 &    Tricky Defector &   0.01875 &                $\pi$ &   0.31686 \\
4  &        PSO Gambler 2 2 2 &   0.02143 &           Cycle Hunter &   0.21538 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
5  &              Evolved ANN &   0.02878 &         Risky QLearner &   0.22222 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
6  &            Evolved ANN 5 &   0.03390 &            Retaliate 3 &   0.22887 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
7  &        PSO Gambler 1 1 1 &   0.03704 &          Cycler CCCCCD &   0.23507 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
8  &            Evolved FSM 4 &   0.04891 &            Retaliate 2 &   0.23913 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
9  &         PSO Gambler Mem1 &   0.05036 &        Defector Hunter &   0.24038 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
10 &                 Winner12 &   0.06011 &              Retaliate &   0.24177 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
11 &             Fool Me Once &   0.06140 &    Hard Tit For 2 Tats &   0.25000 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
12 &                      DBS &   0.07143 &               ShortMem &   0.25286 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
13 &            DoubleCrosser &   0.07200 &    Limited Retaliate 3 &   0.25316 &    Fool Me Forever &   0.07080 &    Cautious QLearner &   0.40909 \\
14 &              BackStabber &   0.07519 &      Limited Retaliate &   0.25706 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
\bottomrule
    \end{tabular}

>>>>

\begin{tabular}{lggllggllggllr}
    \toprule
    & \multicolumn{2}{g}{Standard} & \multicolumn{2}{g}{Noisy (\(p_n \leq 0.1\))} & \multicolumn{2}{g}{Probabilistic ending (\(p_e \leq 0.1\))} &  \multicolumn{2}{c}{Noisy probabilistic ending} \\
    \toprule
    {} &                     Name & $\bar{r}$ &                       Name & $\bar{r}$ &                       Name & $\bar{r}$ &                       Name & $\bar{r}$ \\
    \midrule
    0  &            Evolved HMM 5 &     0.007 &                         DBS &       0.0 &             Evolved FSM 16 &       0.0 &                     Raider &     0.022 \\
    1  &           Evolved FSM 16 &      0.01 &     Evolved FSM 16 Noise 05 &     0.008 &    Evolved FSM 16 Noise 05 &     0.013 &                       MEM2 &     0.037 \\
    2  &     EvolvedLookerUp2\_2\_2 &     0.011 &      Evolved ANN 5 Noise 05 &     0.013 &                       MEM2 &     0.027 &                   Prober 3 &     0.039 \\
    3  &  Evolved FSM 16 Noise 05 &     0.017 &                 BackStabber &     0.024 &              Evolved HMM 5 &     0.043 &    Evolved FSM 16 Noise 05 &     0.048 \\
    4  &        PSO Gambler 2\_2\_2 &     0.022 &               DoubleCrosser &     0.025 &       EvolvedLookerUp2\_2\_2 &     0.049 &                Hard Prober &     0.072 \\
    5  &              Evolved ANN &     0.029 &               Evolved ANN 5 &     0.028 &       Spiteful Tit For Tat &     0.059 &       Spiteful Tit For Tat &     0.078 \\
    6  &            Evolved ANN 5 &     0.034 &                 Evolved ANN &     0.038 &           Nice Meta Winner &     0.069 &          Better and Better &     0.089 \\
    7  &        PSO Gambler 1\_1\_1 &     0.037 &        Spiteful Tit For Tat &     0.051 &         NMWE Finite Memory &     0.069 &                    Grudger &     0.091 \\
    8  &            Evolved FSM 4 &     0.049 &               Evolved HMM 5 &     0.051 &         NMWE Deterministic &      0.07 &                  Fortress4 &     0.096 \\
    9  &         PSO Gambler Mem1 &      0.05 &              Level Punisher &     0.052 &                    Grudger &      0.07 &     Meta Winner Memory One &     0.099 \\
    10 &                 Winner12 &      0.06 &                   Omega TFT &     0.059 &           NMWE Long Memory &     0.074 &           NMWE Long Memory &     0.099 \\
    11 &             Fool Me Once &     0.061 &                Fool Me Once &     0.059 &  Nice Meta Winner Ensemble &     0.076 &           Nice Meta Winner &     0.104 \\
    12 &                      DBS &     0.071 &  PSO Gambler 2\_2\_2 Noise 05 &     0.067 &       EvolvedLookerUp1\_1\_1 &     0.077 &         NMWE Deterministic &     0.109 \\
    13 &            DoubleCrosser &     0.072 &              Evolved FSM 16 &     0.078 &            NMWE Memory One &      0.08 &            NMWE Memory One &     0.112 \\
    14 &              BackStabber &     0.075 &                  EugineNier &      0.08 &            NMWE Stochastic &     0.085 &  Nice Meta Winner Ensemble &     0.115 \\
    \bottomrule
    \end{tabular}
